Forecasting the 2024 U.S. Presidential Election: Polling Trends and Dynamics Based on National General Election Polls

### 2024-11-04 paper/paper.qmd
Updated Paper

library(tidyverse)
library(usmap)
library(dplyr)
library(here)
library(ggplot2)
library(janitor)
library(knitr)
library(flextable)
library(arrow)
```

# Load the cleaned dataset for use in this section
analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")

>>>>

library(tidyverse)
library(usmap)
library(dplyr)
library(here)
library(ggplot2)
library(janitor)
library(knitr)
library(flextable)
library(arrow)
analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))
```
